---
title: "Untitled"
author: "group1"
date: "18/03/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(tidyverse)
library(moderndive)
library(skimr)
library(kableExtra)
library(dplyr)
library(readr)
library(Stat2Data)
library(ggplot2)
library(GGally)
```

## load data from csv files
```{r}
data <- read.csv("dataset1.csv", na.strings = "") %>% rename("Number_of_Family"=7,
                                                             "FoodExpenditure" = 3,
                                                             "Gender" = 4,
                                                             "Age" = 5,
                                                             "Type" = 6,
                                                             "Area" = 8,
                                                             "HouseAge" = 9,
                                                             "bedrooms" = 10)
glimpse(data)
```

$FoodExpenditure$ is the annual expenditure by the household on food (in Philippine peso)
$Gender$ is the head of the households sex
$Age$ is the head of the households age (in years)
$Type$ is the relationship between the group of people living in the house
$Number_of_Family$ is the number of people living in the house
$Area$ is the floor area of the house (in $𝑚^2$)
$HouseAge$ is the age of the building (in years)
$bedrooms$ is the number of bedrooms in the house
$Electricity$ indicates that if the house have electricity? (1=Yes, 0=No)

convert chr into factor
```{r}
data$Region <- factor(data$Region)
data$Gender <- factor(data$Gender)
data$Type <- factor(data$Type)    
```

Check continuous variables
```{r}
continuous <-select_if(data, is.numeric)
summary(continuous)
```

data have totally different scales and many of them have large outliers, may need to standardize them?

```{r}
ggplot(continuous, aes(x = Number_of_Family )) + geom_density(alpha = .2, fill = "yellow")

top_one_percent <- quantile(data$Number_of_Family , .99)
top_one_percent 

data_drop <-data %>%
  filter(Number_of_Family <top_one_percent)
dim(data_drop)
ggplot(data_drop, aes(x = Number_of_Family)) + geom_density(alpha = .2, fill = "yellow")

data_rescale <- data_drop %>%
  mutate_if(is.numeric, funs(as.numeric(scale(.))))
glimpse(data_rescale)
```

99% of the family member is below 11.76, drop the observations above this threshold?

check factor varialbles 
```{r}
factor <- data.frame(select_if(data_rescale, is.factor))
ncol(factor)
```

Create graph for each column
```{r}

data$Number_of_Family <- factor(data$Number_of_Family)

graph <- lapply(names(factor), 
                function(x) 
                  ggplot(factor, aes(get(x))) +
                  geom_bar(width = 0.1) +
                  theme(axis.text.x = element_text(angle = 90)))
```
## Recast Feature
Change level family number as it has too many levels.

ver.1
```{r}
#recast_data <- data_rescale %>%
#  select(-x) %>%
#  mutate(Number_of_Family = factor(ifelse(Number_of_Family == "1" | Number_of_Family == "2" | Number_of_Family == "3" | Number_of_Family == "4" | Number_of_Family == "5" | Number_of_Family == "6", "<7", 
#                                  ifelse(Number_of_Family == "7"| Number_of_Family == "8"| Number_of_Family == "9"| Number_of_Family == "10"| Number_of_Family == "11"| Number_of_Family == "12", "7-12", 
#                                   ifelse( Number_of_Family == "13" | Number_of_Family == "14"| Number_of_Family == "15", ">12")))))
```
ver.2
```{r}
#recast_data <- data_rescale %>%
#  mutate(Number_of_Family = factor(ifelse(Number_of_Family == "1" | Number_of_Family == "2" | Number_of_Family == "3"| Number_of_Family == "4"| Number_of_Family == "5"| Number_of_Family == "6", "<6", 
#                                   ifelse(Number_of_Family == "7" | Number_of_Family == "8" | Number_of_Family == "9"| Number_of_Family == "10"| Number_of_Family == "11"| Number_of_Family == "12", "7-12",
#                                   ifelse(Number_of_Family == "13"| Number_of_Family == "14"| Number_of_Family == "15",">12")))))
```

## Summary Statistic

visualize the correlation between the variables
```{r}
corr <- data.frame(lapply(data, as.integer)) #Convert data to numeric
ggcorr(corr, method = c("pairwise", "spearman"), 
             nbreaks = 8, 
             hjust = 0.9,
             label = TRUE,
             label_size = 2,
             color = "grey50")
```

## Train/test set

split the data between a train set and a test set (for machine learning task if needed)
```{r}
set.seed(1234)
create_train_test <- function(data1, size = 0.8, train = TRUE) {
  n_row = nrow(data1)
  total_row = size * n_row
  train_sample <- 1: total_row
  if (train == TRUE) {
    return (data1[train_sample, ])
  } else {
    return (data1[-train_sample, ])}}

data_train <- create_train_test(data, 0.8, train = TRUE)
data_test <- create_train_test(data, 0.8, train = FALSE)
```

## Generalized Linear Model
```{r}
model <- glm(Number_of_Family~FoodExpenditure+Gender+Age+Type+Area+HouseAge+bedrooms+Electricity, 
             data = data_train, family = 'binomial')
summary(model)
```
The summary of our model reveals interesting information. The performance of a logistic regression is evaluated with specific key metrics.

## Assess the performance of the model

The logistic regression can be evaluated through the output of the glm() function which stored in a list. Below we print the first five elements to see the results.

```{r}
lapply(model, class)[1:5]
model$aic
predict <- predict(model, data_test, type = 'response')
```

```{r}
table_mat <- table(data_test$Number_of_Family, predict > 0.5)
table_mat

```

check model accuracy
```{r}
accuracy_Test <- sum(diag(table_mat)) / sum(table_mat)
accuracy_Test
```


